---
jupyter:
  jupytext:
    formats: ipynb,Rmd
    text_representation:
      extension: .Rmd
      format_name: rmarkdown
      format_version: '1.2'
      jupytext_version: 1.11.4
  kernelspec:
    display_name: R
    language: R
    name: ir353
---

```{r, include=FALSE}
knitr::opts_knit$set(root.dir = here::here())
```

```{r}
setwd(here::here())
```

```{r}
library("metacell")
library("Matrix")
library("dplyr")
```

```{r}
scdb_init("scrna_db/", force_reinit = TRUE)
```

### Import Tet TKO chimera plates into metacell
This notebook requires that the UMI tables for each plate are available in the folder **data/umi.tables** . If they are not available, please run the cell below to download the necessary data

```{r}
# If you need to download the umi tables, please run the two lines below
if (0) {
    source("../scripts/download_data.R")
    download_umi_tables()
}
```

```{r}
source("scripts/pipeline/import_plates.R")
```

```{r}
mat_nm <- "tko_chim"

metadata <- read.csv(file = "data/plate_metadata.csv", stringsAsFactors = F)
genotype <- "TKO"
treatment <- c("Chimera assay")
metadata <- metadata[metadata$treatment %in% treatment, ]
metadata <- metadata[grep(pattern = genotype, x = metadata$genotype), ]

# remove additionally the plate 190730_P03. No embryo and facs data available. Only relevant for TKO Chimera
metadata <- metadata[metadata$plate != "190730_P03", ]

import_plates(mat_nm = mat_nm, metadata = metadata)
```

### Import Tet TKO tetraploid-complemented embryos

```{r}
mat_nm <- "tko_tetra"

metadata <- read.csv(file = "data/plate_metadata.csv", stringsAsFactors = F)
genotype <- "TKO"
treatment <- c("Tetraploid complementation assay")
metadata <- metadata[metadata$treatment %in% treatment, ]
metadata <- metadata[grep(pattern = genotype, x = metadata$genotype), ]

import_plates(mat_nm = mat_nm, metadata = metadata)
```

```{r}
# There are four mixed plates containing both tetraploid-complemented control and Tet TKO embryos
# We additionally ignore the cells from control embryos
mat <- scdb_mat("tko_tetra")

ctrl_cells <- mat@cell_metadata$cell[grep(pattern = "Ctrl", x = mat@cell_metadata$embryo)]

mat <- scm_ignore_cells(scmat = mat, ig_cells = union(mat@ignore_cells, ctrl_cells))

scdb_add_mat(id = "tko_tetra", mat = mat)
```

### Import Control tetraploid-complemented embryos

```{r}
mat_nm <- "control_tetra"

metadata <- read.csv(file = "data/plate_metadata.csv", stringsAsFactors = F)
genotype <- "Control"
treatment <- c("Tetraploid complementation assay")
metadata <- metadata[metadata$treatment %in% treatment, ]
metadata <- metadata[grep(pattern = genotype, x = metadata$genotype), ]

import_plates(mat_nm = mat_nm, metadata = metadata)
```

```{r}
# There are four mixed plates containing both tetraploid-complemented control and Tet TKO embryos
# We additionally ignore the cells from TKO embryos
mat <- scdb_mat("control_tetra")

tko_cells <- mat@cell_metadata$cell[grep(pattern = "TKO", x = mat@cell_metadata$embryo)]
length(tko_cells)

mat <- scm_ignore_cells(scmat = mat, ig_cells = union(mat@ignore_cells, tko_cells))

scdb_add_mat(id = "control_tetra", mat = mat)
```

### Import Tet 1/2 DKO chimera embryos

```{r}
mat_nm <- "dko12_chim"

metadata <- read.csv(file = "data/plate_metadata.csv", stringsAsFactors = F)
genotype <- "Tet1/2 DKO"
treatment <- c("Chimera assay")
metadata <- metadata[metadata$treatment %in% treatment, ]
metadata <- metadata[grep(pattern = genotype, x = metadata$genotype), ]

import_plates(mat_nm = mat_nm, metadata = metadata)
```

### Import Tet 1/3 DKO chimera embryos

```{r}
mat_nm <- "dko13_chim"

metadata <- read.csv(file = "data/plate_metadata.csv", stringsAsFactors = F)
genotype <- "Tet1/3 DKO"
treatment <- c("Chimera assay")
metadata <- metadata[metadata$treatment %in% treatment, ]
metadata <- metadata[grep(pattern = genotype, x = metadata$genotype), ]

import_plates(mat_nm = mat_nm, metadata = metadata)
```

### Import Tet 2/3 DKO chimera embryos

```{r}
mat_nm <- "dko23_chim"

metadata <- read.csv(file = "data/plate_metadata.csv", stringsAsFactors = F)
genotype <- "Tet2/3 DKO"
treatment <- c("Chimera assay")
metadata <- metadata[metadata$treatment %in% treatment, ]
metadata <- metadata[grep(pattern = genotype, x = metadata$genotype), ]

import_plates(mat_nm = mat_nm, metadata = metadata)
```

### Import AAV-Cre delivered whole-embryo TKOs

```{r}
mat_nm <- "tko_germline"

metadata <- read.csv(file = "data/plate_metadata.csv", stringsAsFactors = F)
genotype <- "TKO"
treatment <- c("AAV Cre-delivered Tet1/2/3 triple KO")
metadata <- metadata[metadata$treatment %in% treatment, ]
metadata <- metadata[grep(pattern = genotype, x = metadata$genotype), ]

import_plates(mat_nm = mat_nm, metadata = metadata)
```

```{r}
#### next step: gating of populations
```

```{r}

```
