---
jupyter:
  jupytext:
    formats: ipynb,Rmd
    text_representation:
      extension: .Rmd
      format_name: rmarkdown
      format_version: '1.2'
      jupytext_version: 1.11.4
  kernelspec:
    display_name: R
    language: R
    name: ir353
---

```{r, include=FALSE}
knitr::opts_knit$set(root.dir = here::here())
```

```{r}
setwd(here::here())
```

```{r}
library("metacell")
library("tgstat")
library("tgconfig")
library("Matrix")
library("dplyr")
```

```{r}
scdb_init("scrna_db/", force_reinit = T)
```

```{r}
mat <- scdb_mat("tko_tetra")
```

#### Remove extraembryonic ectoderm and parietal endoderm cells

```{r}
source("scripts/pipeline/remove_exe_ectoderm_and_parietal_endo_cls.R")
mat <- remove_exe_ectoderm_and_parietal_endoderm(mat_query = mat)
```

#### Merge cells with the wildtype atlas

```{r}
source("scripts/pipeline/merge_umi_mat_with_wt10_umi_mat.R")
mat_new <- merge_umi_mat_with_wt10(scmat = mat)
scdb_add_mat(id = "tko_tetra_wt10", mat = mat_new)
```

#### Generate single-cell balanced kNN-graph
This step needs the file  
_data/tet_tko.bad_genes.txt_

```{r}
source("scripts/pipeline/gen_cgraph.R")
gen_cgraph(mat_nm = "tko_tetra_wt10", force_recompute_cgraph = F)
```

#### Transfer cell type annotation to TKO cells

```{r}
source("scripts/pipeline/transfer_cell_type_annotation.R")
transfer_color_chimera_tetraploid(mat_nm = "tko_tetra_wt10")
```

#### Time tetraploid-complemented embryos based on their injected TKO cells

```{r}
source("scripts/pipeline/transfer_time_annotation.R")
source("scripts/pipeline/tetraploid_timing.R")
tetra_timing("tko_tetra_wt10")
```

#### Export infered time and cell type into table

```{r}
source("scripts/pipeline/create_metadata.R")
create_tko_tetraploid_metadata()
```

#### Generate a separate UMI matrix and metacell object for the TKO cells

```{r}
source("scripts/pipeline/generat_ko_mat.R")
generate_ko_mat_tetraploid()
```

```{r}
source("scripts/pipeline/generic_mc.R")
tgconfig::override_params(config_file = "config/tet_chim.yaml", package = "metacell")

bad_genes <- read.table("data/tet_tko.bad_genes.txt", sep = "\t", stringsAsFactors = F)
bad_genes <- bad_genes[, 1]

mat_nm <- "tko_tetra_ko"

generate_mc(mat_nm, add_bad_genes = bad_genes)
```

```{r}
wt_atlas <- mcell_gen_atlas(
    mat_id = "sing_emb_wt10",
    mc_id = "sing_emb_wt10_recolored",
    gset_id = "sing_emb_wt10",
    mc2d_id = "sing_emb_wt10_recolored"
)

cmp <- mcell_proj_on_atlas(
    mat_id = "tko_tetra_ko",
    mc_id = "tko_tetra_ko",
    atlas = wt_atlas,
    fig_cmp_dir = paste0("figs/atlas_projection_", "tko_tetra_ko"), recolor_mc_id = "tko_tetra_ko", ten2mars = F
)
```

```{r}
tgconfig::set_param(param = "mcell_mc2d_T_edge", value = 0.03, package = "metacell")
mcell_mc2d_force_knn(mc2d_id = "tko_tetra_ko", mc_id = "tko_tetra_ko", graph_id = "tko_tetra_ko", graph_parametric = T, feats_gset = "tko_tetra_ko")
mcell_mc2d_plot("tko_tetra_ko")
```

```{r}

```

```{r}

```
